---
title: "Developing-Data-Products-Week-2-Assignment"
date: "02/05/2021"
output: html_document
    
---

### Data set
The data used is from from an actual operating wind farm, but identifying info is removed. I used this data 
from my current work. Source code and data located github [link](https://github.com/barteec/Developing-Data-Products-Week-2-Assignment) I have loaded
this data into a folder called [datafiles](https://github.com/barteec/Developing-Data-Products-Week-2-Assignment). Please 
be sure to load this file folder to you working directory. 

Please make sure you have these libraries loaded:
```{r warning=FALSE, message=FALSE}
library(knitr)
library(dplyr)
library(leaflet)
library(htmltools)
library(kableExtra)
library(lubridate)
library(ggplot2)
library(data.table)
```

```{r libraries, include=FALSE, echo=FALSE}
library(knitr)
library(dplyr)
library(leaflet)
library(htmltools)
library(kableExtra)
library(lubridate)
library(ggplot2)
library(data.table)

setwd(getwd()) # will default to your WD
#make sure you load the datafiles folder from github
#Load data. Make sure you loaded the csv files from the github. 
WinData <- read.csv(file = "./datafiles/WinData.csv")
WinInfo <- read.csv(file = "./datafiles/WinInfo.csv")
WinLoc <- read.csv(file = "./datafiles/WinLoc.csv")

```

## General Wind Farm Information and Map Location
Below you will see general identifying information for a Wind Farm located in North Dakota, USA. I used the geo-tags 
(lat,long) for each wind turbine. This wind farm was used to complete and show the ability to use R Markdown that features 
a map created with Leaflet.

Some things to take notice when viewing the map:

* The R code is set to pick a random wind turbine of 56 in the wind farm to show as a red map icon, while all others are blue

* Map is interactive where you can zoom in and out

* If you are interested  in the wind turbines there is link in the Information table for you.

```{r information table1, echo=FALSE, results="asis", warning=FALSE}
cat(paste0("<table width='100%'><tr style='width:100%'>",
           "<td style='width:50%;padding-right:10px;'>"))

Parkdata <- data.table(WinInfo)
Parkdata <- melt.data.table(Parkdata, id.vars = "ï..ID_WF")
Parkdata <- setnames(Parkdata, c("variable", "value"), c("Category", "Information"))
Parkdata <- Parkdata[,!1, with = F]


kable(Parkdata, format = "markdown")
cat("<font size='2'>*Data used is from an acutal operating wind farm but identifying info is removed.</font>")
cat("</td>")

```



```{r map, results="asis", echo=FALSE}
# ensure you loaded the folder icons from git hub
turbinesFarmData <- data.table(WinLoc)

cat("<td style='width:50%;padding-left:10px;'>")
coloredIcons <- makeIcon(
  iconUrl = ifelse(turbinesFarmData$Winturbine == paste("WTG", sample(1:56, 1)), #just picks random turbine to show in red
                   "./datafiles/icons/red_icon.png",
                   "./datafiles/icons/blue_icon.png"),
                    iconWidth=25,
                    iconHeight=43,
                    iconAnchorX=17,
                    iconAnchorY=38,
                    popupAnchorX=1,
                    popupAnchorY=-40
                  )

turbines <- turbinesFarmData %>% filter(!is.na(lat) & !is.na(long))

map <-
  leaflet() %>%
  addProviderTiles(providers$Esri.NatGeoWorldMap)

if (nrow(turbines) > 0) {
  map <- addMarkers(map = map,
                    data = turbines,
                    ~ long,
                    ~ lat,
                    icon = coloredIcons,
                    popup = paste(turbinesFarmData$ï..Wind.Farm,
                                  turbinesFarmData$Winturbine,
                                  sep="<br>"))
}
map$width <- "150%"
map$height <- "450px"
map
cat("</td></tr></table>")
```
<div>


## Plot to show the past year's Wind Speed vs Power Ouput
Th plot below is a very basic representation of a power curve chart for a wind turbine. You will see how wind speed 
and power are graphed against one another. You can see as wind speed increases the power output will increase (ramp up) 
as well. The wind turbine will max out power output at 3 megawatts (mw) and will slow and/or stop producing power as 
wind speed increases past 20 meters per second (m/s) 
```{r echo=FALSE, results= 'asis', warning=FALSE, message = FALSE}
#--- --- --- Wind Speed, power and temps

Plot <- data.table(WinData)
Plot <- setnames(Plot, "ï..ActivePowerAvg", "ActivePowerAvg")
Plot <- Plot[ActivePowerAvg > 0]


PKhc <- ggplot(Plot, aes(x = WindSpeedAvg, y= ActivePowerAvg)) + 
        geom_point(shape = 18, color = "#8181F7")+
        scale_x_discrete(limits = 0:30)+
        scale_y_discrete(limits = seq(0, 3000, by=500))+
        theme_light()+
        labs(title = "Wind Speed vs Power Output",
             subtitle = "power in mwh")+
        theme(
          plot.title = element_text(hjust = 0.5, size = 14),    # Center title position and size
          plot.subtitle = element_text(hjust = 0.5),            # Center subtitle
          plot.caption = element_text(hjust = 0, face = "italic"), # move caption to the left
        )


PKhc
```
