---
title: "Developing-Data-Products-Week-3-Assignment"
author: Bently
date: "02/05/2021"
output: ioslides_presentation
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(kableExtra)
library(plotly)
library(data.table)
```

## Data set
The data used is from from an actual operating wind farm, but identifying info is removed. I used this data from my current work. Source code and data located github [link](https://github.com/barteec/DevelopingDataProducts-Week3-Assignment)
```{r  include=TRUE, echo=FALSE}

setwd(getwd()) # will default to your WD
#make sure you load the datafiles folder from github
#Load data. Make sure you loaded the csv files from the github. 
WinData <- readxl::read_xlsx(path = "./PowerCurveSummary.xlsx", sheet = 1)
WinInfo <- read.csv(file = "./WinInfo.csv")
```


## General Wind Farm Information and Map Location
If you are interested  in the wind turbines there is link in the Information table for you
```{r echo=FALSE, results="asis", warning=FALSE}

Parkdata <- data.table(WinInfo)
Parkdata <- melt.data.table(Parkdata, id.vars = "ï..ID_WF")
Parkdata <- setnames(Parkdata, c("variable", "value"), c("Category", "Information"))
Parkdata <- Parkdata[,!1, with = F]
kable(Parkdata)
```



## Plot to show the past year's Wind Speed vs Power Ouput
<font size="3">Reference Power advertised by manufacture versus the Measured Power</font>
```{r echo=FALSE, results= 'asis', warning=FALSE, message = FALSE}


Plot <- WinData

fig1 <- plot_ly(data = Plot, x = ~Wind_Speed, y = ~Reference_Power, fill = 'tozeroy',
        # Hover text:
        text = ~paste("Wind_Speed: ", Wind_Speed, 'Reference_Power', Reference_Power),
        color = ~Reference_Power, size = ~Reference_Power
        ) 
fig2 <- plot_ly(data = Plot, x = ~Wind_Speed, y = ~Measured_Power, fill = 'tozeroy',
        # Hover text:
        text = ~paste("Wind_Speed: ", Wind_Speed, 'Measured_Power', Measured_Power),
        color = ~Measured_Power, size = ~Measured_Power
        )
fig <- subplot(fig1, fig2) %>% layout(title = "Reference_Power compared to Measured_Power")
fig
```


## Plot to show the past year's Wind Speed vs Power Ouput
<font size="3">Reference Power advertised by manufacture versus the Measured Power</font>
```{r echo=FALSE, results= 'asis', warning=FALSE, message = FALSE}
fig3 <- plot_ly(y = Plot$Reference_Power, type = "box", boxpoints = "all", jitter = 0.3,
        pointpos = -1.8, name="Reference_Power")
fig3 <- fig3 %>% add_trace(y = Plot$Measured_Power, name="Measured_Power")
fig3 <- fig3 %>% layout(title = "Reference_Power compared to Measured_Power")
fig3
```
